### 2016-01-20 paper.tex
Use lambda_0 for optimal TSR

While operating at its optimal tip speed ratio $\lambda=3.1$ the wake at
$x/D=0.93$ downstream was shown to be relatively symmetrical and lacked the
evidence of strong blade stall, both of which differentiate this near-wake from
the higher solidity, lower optimal $\lambda$ UNH-RVAT. Terms from the mean
kinetic energy transport equation were also computed in this $y$--$z$ plane,
showing the relative importance of the vertical advection compared with
turbulent transport terms at this location. It is interesting to note that
though the RM2 is a more effective energy converter than the UNH-RVAT, its wake
recovery may in fact be delayed due to weaker blade tip vortex shedding and
lower levels of turbulence in the near-wake.

>>>>

While operating at its optimal tip speed ratio $\lambda=3.1$ the wake at
$x/D=0.93$ downstream was shown to be relatively symmetrical and lacked the
evidence of strong blade stall, both of which differentiate this near-wake from
the higher solidity, lower $\lambda_0$ UNH-RVAT. Terms from the mean kinetic
energy transport equation were also computed in this $y$--$z$ plane, showing the
relative importance of the vertical advection compared with turbulent transport
terms at this location. It is interesting to note that though the RM2 is a more
effective energy converter than the UNH-RVAT, its wake recovery may in fact be
delayed due to weaker blade tip vortex shedding and lower levels of turbulence
in the near-wake.
